A Spiking Independent Accumulator Model for Winner-Take-All Computation

### 2017-04-17 doc/paper/paper.tex
Rewrite memory model example.

In contrast, the IA network is better suited for situations where a discrete sequence of decisions is required.
After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
However, once a decision is made, the network provides a stable output.
As an example, we intend to use the IA network in a free recall memory model where a clear response needs to be selected.
A non-correct response in this case might still be a valid response in the context of this task and could be better than no response at all.

>>>>

In contrast, the IA network is better suited for situations where a discrete sequence of decisions is required.
After selecting a winner, the model's decision will persist due to self-excitation, even in the absence of input.
Thus, after making a decision, it is necessary to reset the model by inhibiting the winning accumulator.
This limits how quickly successive decisions can be made and reduces the ability to react to changing inputs.
However, once a decision is made, the network provides a stable output.
As an example, we intend to use the IA network in a free recall memory model where a clear selection of successive responses needs to be made, but correctly identifying the single item remembered most strongly is not required.
